Differences in Homicide Case Information Indicates Why Justice is Not Served

### 2024-12-03 paper/paper.qmd
Finished results section

```{r}
#| label: fig-model-result-ci
#| fig-cap: The credible intervals (line) for coefficient estimates (dot) of predictor variables for homicides that go unsolved from 2010 to 2017.
#| echo: false
#| warning: false
#| message: false
# Specify credible interval to be 90% and present model results
modelplot(unsolved_model_results, conf_level = 0.9) +
  labs(x = "90 per cent credible interval")
```
@tbl-model-result and @fig-model-result-ci

>>>>

```{r}
#| label: fig-model-result-ci
#| fig-cap: The credible intervals (line) for coefficient estimates (dot) of predictor variables for homicides that go unsolved from 2010 to 2017.
#| echo: false
#| warning: false
#| message: false
# Specify credible interval to be 90% and present model results
modelplot(unsolved_model_results, conf_level = 0.9) +
  labs(x = "90 per cent credible interval")
```
@tbl-model-result and @fig-model-result-ci presents the results from our logistic regression model in the Bayesian framework and the 90% credible intervals of each predictor, respectively. From @tbl-model-result, the intercept $\beta_0$ of -165.865 indicates that when the homicide victim is White, since "White" is the baseline for the victim_race predictor, and victim_age is 0 and year being 2010 with its coefficient being 0 and the victim's sex is female, the homicide is more likely to be solved. @tbl-model-result indicates that the coefficient estimate of victim_race $\beta_1$ is 0.168 when the victim is Asian. This means that the log-odds of a homicide case being unsolved increases by 0.168 when the victim is Asian while other predictor variables stays fixed. Following this, when the victim's race is Black or Hispanic, the log-odds of a homicide being unsolved increases by 0.567 and 0.434, respectively. This indicates that the likelihood of a homicide going unsolved increases if the victim's race is Asian, Black, or Hispanic relative to a victim's race being White. On the other hand, when the victim's race falls under "Other", the log-odds of a homicide case being unsolved decreases by 0.296. This indicates that the likelihood of a homicide being unsolved decreases if the victim's race falls under "Other" relative to a victim's race being White. However, since the 90% credible interval for the coefficient estimate of victim_race appears to be close 0 as seen in @fig-model-result-ci, this means that a victim's race has a weak likelihood of impacting the outcome of their case being unsolved.

@tbl-model-result shows that since the coefficient estimate of victim_age $\beta_2$ is -0.006, this means the log-odds of a homicide case being unsolved decreases by 0.006 when the age of the victim increases by 1 year as other predictor variables stay constant. This means victims of unsolved homicides are likely on the more younger side. @fig-model-result-ci also indicates that $\beta_2$'s 90% credible interval is close to 0 or includes 0 in its interval, indicating there is a chance the victim's age does not have an influence the outcome of a homicide case being unsolved. With the coefficient estimate of victim_sex $\beta_3$ being 0.662 in @tbl-model-result, it indicates that the log-odds of a homicide case being unsolved increases by 0.662 when the victim is male while other predictors are fixed. This suggests that the likelihood of the a homicide case being unsolved increases when the victim is a male. Looking at @fig-model-result-ci, the credible interval for $\beta_3$ is also slightly above 0. @tbl-model-result also shows that the log-odds of a homicide being unsolved decreases by 1.089 as indicated by the coefficient estimate $\beta_4$ when city is set to Los Angeles with other predictors being fixed. This indicates that more unsolved homicide cases are likely to occur in Chicago instead. @fig-model-result-ci also shows that $\beta_4$'s credible interval is below 0. Looking at the year predictor and its coefficient estimate, the log-odds of a homicide case being unsolved increases by 0.083 as noted by the coefficient estimate $\beta_5$ when the year increases by 1 year while the other predictors stay constant. This indicates that cases are more likely to be unsolved in the later years between 2010 to 2017. @fig-model-result-ci also shows that $\beta_5$'s credible interval is slightly above 0 or includes 0 indicating that the year has a weak likelihood of indicating if a homicide is unsolved.
